---
title: "Trains"
author: "Oluchi Nnadi"
format: html
execute:
  echo: false
---

```{r}
#| message: false
library(tidyverse)
library(primer.data)
```

```{r}
ggplot(trains, aes(x = treatment, y = att_end)) +
  geom_jitter(width = 0.2, height = 0.2, alpha = 0.5) +
  stat_summary(fun = "mean", geom = "point", color = "red", size = 4) +
  labs(
    title = "Attitude Toward Immigration After Intervention",
    subtitle = "Comparing participants who saw Spanish-speakers (Treated) vs. those who did not (Control)",
    x = "Treatment Group",
    y = "Attitude Toward Immigration (att_end)",
    caption = "Source: primer.data::trains"
  ) +
  theme_minimal()
```



```{r}
glimpse(trains)
```

Summary: Within the U.S., attitude towards immigration can vary widely due to various factors; one such factor is the exposure to people speaking other languages. Using data from Enos's experiment that measured the attitude of Boston-area Metra commuters who were and weren't exposed to Spanish-speaking confederates on the morning train, we aim to measure the average causal effect of Spanish exposure on immigration views.